---
title: "Week 5 code along_penguin size"
author: "Joaquin Meckler"
date: "11/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(effsize)
library(broom)
library(ggbeeswarm)
library(car)
```

## T-Tests

mass: comparison between male and female penguins

```{r}
chinstrap<-penguins %>% 
  filter(species=="Chinstrap")

# Histograms

ggplot(data=chinstrap, aes(x=body_mass_g))+
  geom_histogram(bins=10)+
  facet_wrap(~sex)

# QQ plot

ggplot(data=chinstrap, aes(sample = body_mass_g))+
  geom_qq()+
  facet_wrap(~sex)

# discriptive statistics

chinstrap %>% 
  group_by(sex) %>% 
  summarize(
    mean_mass=mean(body_mass_g),
    median_mass=median(body_mass_g),
    sd_mass=sd(body_mass_g),
    sample_size=n()
  )
```

get vectors of body_mass_g for M/F

```{r}
chinstrap_f<-chinstrap %>% 
  filter(sex== "female") %>% 
  pull(body_mass_g)


chinstrap_m<-chinstrap %>% 
  filter(sex== "male") %>% 
  pull(body_mass_g)
```

### 2 sample T test

1. is there a significant difference between male and female body mass?

```{r}
chinstrap_ttest<-t.test(chinstrap_f, chinstrap_m)

chinstrap_ttest

cohen.d(chinstrap_f, chinstrap_m)
```


are male chinstraps significantly larger then female chinstraps

```{r}
t.test(chinstrap_m,chinstrap_f, alternative = "greater")
```


### One-way anova

table of counts by species and sex
```{r}
penguins_count<-penguins %>% 
  count(species,sex)
```

create subset of F penguins

```{r}
penguin_f<-penguins %>% 
  filter(sex=="female")
```


```{r}
ggplot(data = penguin_f, aes(x=flipper_length_mm))+
  geom_histogram(aes(fill=species))+
  facet_wrap(~species, scales="free")
```


```{r}
ggplot(data = penguin_f, aes(sample=flipper_length_mm))+
  geom_qq(aes(color=species))+
  facet_wrap(~species, scales="free")
```


## summary stats

```{r}
penguin_f_summary <- penguin_f %>% 
  group_by(species) %>% 
  summarize(
    mean_flipper_length=mean(flipper_length_mm),
    sd_flipper_length=sd(flipper_length_mm),
    sample_size=n(),
    var_flipper_length=var(flipper_length_mm),
    se_flipper_length=sd(flipper_length_mm)/sqrt(n()))

leveneTest(flipper_length_mm~species, data=penguin_f)
    
```


### beeswarm plot with me +- 1 sd

```{r}
ggplot()+geom_beeswarm(data=penguin_f,
                       aes(x=species,
                           y=flipper_length_mm),
                       color="darkblue",
                       size=3,
                       alpha=.25)+
  geom_point(data=penguin_f_summary,
             aes(x=species, y=mean_flipper_length),
             size=4.5)+
  geom_errorbar(data=penguin_f_summary, aes(x=species,
                                            ymax=mean_flipper_length+sd_flipper_length,
                                            ymin=mean_flipper_length-sd_flipper_length),
                width=.1)+
  theme_bw()
```

##one-way anove

```{r}
penguin_aov<-aov(flipper_length_mm ~species, data=penguin_f)
summary(penguin_aov)

TukeyHSD(penguin_aov)
```
### type III anova with carpackage

```{r}
penguin_lm<-lm(flipper_length_mm~species, data=penguins_f)

penguin_aov_t3<-Anova(penguin_lm, type="III")
penguin_aov_t3
```












